---
title: "Investigating the association of inflammatory-related exposures and risk of epithelial ovarian cancer by tumor immune profiles"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    toc_collapsed: false
    theme: cerulean
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
h1.title {
  font-size: 25px;
}
.figure {
   margin-top: 25px;
   margin-bottom: 25;
}

table {
    margin-top: 25px;
    margin-bottom: 10px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Association between pre-diagnostic inflammatory-related exposures and immune cell abundance</span>

</div>
<br>

```{r library, include=FALSE}
library(tidyverse)
library(fastDummies)
library(data.table)
library(labelled)
library(nnet)
library(gtsummary)
library(ggplot2)
library(survival)
library(survminer)
library(mclust)
library(gplots)
library(riskclustr)
```

```{r load}
OCWAA_markers <- readRDS(paste0(here::here(), "/OCWAA_markers_category.rds")) %>% 
  select(suid, slide_type, casecon, everything()) %>% 
  ungroup() %>% 
  # Filter AACES patients
  filter(!is.na(casecon)) %>% 
  mutate(slide_type_considered = coalesce(slide_type.x, slide_type.y))
```

```{r}
var_label(OCWAA_markers) <- list(refage ~ "Age at diagnosis", refage_cat ~ "Age at diagnosis category",
                           smokcurrent ~ "Smoking status"
) 
```


# I. Data exploration
## 1. Compare patient characteristics for patients with vs. without immune data (Case only)
```{r Compare patient}
OCWAA_markers %>%
  filter(casecon == "Case") %>%
  mutate(have_immune_data = case_when(
    !is.na(slide_type)                   ~ "Have immune data",
    TRUE                                 ~ "No immune data"
  )) %>%
  select(site, diagyear, refage, refage_cat,
         histotype, histotype1, histotype2,
         smokever, smokcurrent,
         packyrs, packyrs_cat,
         BMI_recent_grp, BMI_YA_grp, BMI_YA_2grp,
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta,
         inactive, paga, loc, tertile_loc,
         education,diidensity, diidenswithsupp,
         famhist_br_ov,
         perceived_discrim, phys_trust,
         have_immune_data) %>%
  tbl_summary(by = have_immune_data,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels() %>%
  add_overall() %>% add_p() %>% bold_p(t= .05)
```

## 2. Compare patient characteristics for ROI vs. TMA (Case only with immune data)
```{r Compare ROI vs TMA}
OCWAA_markers %>%
  filter(casecon == "Case") %>%
  mutate(have_immune_data = case_when(
    !is.na(slide_type)                   ~ "Have immune data",
    TRUE                                 ~ "No immune data"
  )) %>%
  filter(have_immune_data == "Have immune data") %>%
  select(site, diagyear, refage, refage_cat,
         histotype, histotype1, histotype2,
         smokever, smokcurrent,
         packyrs, packyrs_cat,
         BMI_recent_grp, BMI_YA_grp, BMI_YA_2grp,
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta,
         inactive, paga, loc, tertile_loc,
         education,diidensity, diidenswithsupp,
         famhist_br_ov,
         perceived_discrim, phys_trust,
         have_immune_data, slide_type_considered) %>%
  tbl_summary(by = slide_type_considered,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)
             ) %>%
  bold_labels() %>%
  add_overall() %>% add_p() %>% bold_p(t= .05)
```

```{r Clean pop}
markers <- OCWAA_markers %>%
  filter(casecon == "Control" | !is.na(slide_type)) %>% 
  mutate(prop_tumor = case_when(
    casecon == "Control"                      ~ 0,
    TRUE                                      ~ mean_tumor.i
  ))
```

### From here, the analysis include control + case patients with immune data patients only.

## 3. Patient characteristics
```{r patient table}
markers %>%
  select(site, diagyear, refage, refage_cat,
         histotype, histotype1, histotype2,
        casecon) %>%
  tbl_summary(by = casecon,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)) %>%
      # modify_header(list(label ~ "**Patient characteristics**", all_stat_cols() ~ "**{level}**, N = {n}")) %>%
  bold_labels() %>%
  add_overall() %>% add_p() %>% bold_p(t= .05)
```

## 4. Immune characteristics (Cases)
```{r Immune table}
markers %>%
  filter(casecon == "Case") %>%
  select(starts_with("CD"), immunoscore_2018lancet_patients) %>%
  tbl_summary(
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)) %>%
      # modify_header(list(label ~ "**Patient characteristics**", all_stat_cols() ~ "**{level}**, N = {n}")) %>%
  bold_labels()
```

## 5. Distribution of the potential inflammatory-related pre-diagnostic exposures in the overall study population and by immune abundance (only use overall intratumoral and overall peritumoral), immune signatures, and immunoscore

### Summary table
```{r exposures table}
markers %>%
  select(smokever, smokcurrent,
         packyrs, packyrs_cat,
         BMI_recent_grp, BMI_YA_grp, BMI_YA_2grp,
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta,
         inactive, paga, loc, tertile_loc,
         education,diidensity, diidenswithsupp,
         famhist_br_ov,
         perceived_discrim, phys_trust,
         casecon) %>%
  tbl_summary(by = casecon,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)
  ) %>%
  # modify_header(list(label ~ "**Patient Exposure characteristics**", all_stat_cols() ~ "**{level}**, N = {n}")) %>%
  bold_labels() %>%
  add_overall() %>% add_p() %>% bold_p(t= .05)

markers %>%
  filter(casecon == "Case") %>%
  select(smokever, smokcurrent,
         packyrs, packyrs_cat,
         BMI_recent_grp, BMI_YA_grp,
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta,
         inactive, paga, loc, tertile_loc,
         education,diidensity, diidenswithsupp,
         perceived_discrim, phys_trust,
         casecon, slide_type_considered) %>%
  tbl_summary(by = slide_type_considered,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)
  ) %>%
  # modify_header(list(label ~ "**Patient Exposure characteristics**", all_stat_cols() ~ "**{level}**, N = {n}")) %>%
  bold_labels() %>%
  add_overall() %>% add_p() %>% bold_p(t= .05)
```

### Intratumoral CD3 total - Overall pop
```{r}
markers %>%
  distinct(suid, .keep_all = TRUE) %>%
  select(smokever, smokcurrent,
         packyrs, packyrs_cat,
         BMI_recent_grp, BMI_YA_grp, BMI_YA_2grp,
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta,
         inactive, paga, loc, tertile_loc,
         education,diidensity, diidenswithsupp,
         famhist_br_ov,
         perceived_discrim, phys_trust,
         CD3_total.i) %>%
  tbl_summary(by = CD3_total.i,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              # type = list(c(diab,
              #   talcever, talcgen, talcnongen,
              #               aspirin, NSAID,aceta,
              #               hyster, hyster1yr,
              #               hyster2yr, hystertype,
              #               tubelig, endomet, fibroids,
              #               pid, education) ~ "categorical"),
              digits = list(all_continuous() ~ 1)
  ) %>% bold_labels() %>% 
  add_overall() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
```

### Intratumoral CD3CD8 total - Overall pop
```{r}
markers %>%
  distinct(suid, .keep_all = TRUE) %>%
  select(smokever, smokcurrent,
         packyrs, packyrs_cat,
         BMI_recent_grp, BMI_YA_grp, BMI_YA_2grp,
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta,
         inactive, paga, loc, tertile_loc,
         education,diidensity, diidenswithsupp,
         famhist_br_ov,
         perceived_discrim, phys_trust,
         CD3_CD8_total.i) %>%
  tbl_summary(by = CD3_CD8_total.i,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)
  ) %>% bold_labels() %>%
  add_overall() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
```

### Intratumoral Immunoscore - Overall pop
```{r}
markers %>%
  distinct(suid, .keep_all = TRUE) %>%
  select(smokever, smokcurrent,
         packyrs, packyrs_cat,
         BMI_recent_grp, BMI_YA_grp, BMI_YA_2grp,
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta,
         inactive, paga, loc, tertile_loc,
         education,diidensity, diidenswithsupp,
         famhist_br_ov,
         perceived_discrim, phys_trust,
         immunoscore_2018lancet_patients) %>%
  tbl_summary(by = immunoscore_2018lancet_patients,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)
  ) %>% bold_labels() %>%
  add_overall() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
```

```{r}
exposure_var <- c("smokever", "smokcurrent",
                  "packyrs", "packyrs_cat", 
                  "BMI_recent_grp", "BMI_YA_grp", "BMI_YA_2grp",
                  "BMI_recent_5", "BMI_YA_5",
                  "endomet", "pid", "fibroids",
                  "talcever", "talcgen", "talcnongen",
                  "diab", "hrtdis", "hbp", "hchol",
                  "aspirin", "NSAID", "aceta", 
                  "inactive", "paga", "loc", "tertile_loc",
                  "education","diidensity", "tertile_diidensity",
                  "diidenswithsupp", "famhist_br_ov",
                  "perceived_discrim", "phys_trust"
                  ) 
```

<!-- <!-- ### Violin plots --> -->
<!-- <!-- ```{r violin} --> -->
<!-- <!-- violin_plot <- function(data, type){ --> -->

<!-- <!--   for (i in exposure_var){ --> -->

<!-- <!--     if(class(markers[[i]]) == "factor" | class(markers[[i]]) == "character") { --> -->

<!-- <!--       p1 <- markers %>% --> -->
<!-- <!--         filter(!is.na(.data[[i]])) %>% --> -->
<!-- <!--         ggplot()+ --> -->
<!-- <!--         geom_violin(aes(x=.data[[i]], y= .data[[paste0(type, ".i")]]), scale = "count")+ --> -->
<!-- <!--         geom_boxplot(aes(x=.data[[i]], y= .data[[paste0(type, ".i")]]), width=.1) + --> -->
<!-- <!--         theme_classic()+ --> -->
<!-- <!--         labs(y=NULL, title="Intratumoral \nROIs") --> -->
<!-- <!--       p2 <- markers %>% --> -->
<!-- <!--         filter(!is.na(.data[[i]])) %>% --> -->
<!-- <!--         ggplot()+ --> -->
<!-- <!--         geom_violin(aes(x=.data[[i]], y= .data[[paste0(type, ".p")]]), scale = "count")+ --> -->
<!-- <!--         geom_boxplot(aes(x=.data[[i]], y= .data[[paste0(type, ".p")]]), width=.1) + --> -->
<!-- <!--         theme_classic()+ --> -->
<!-- <!--         labs(y=NULL, title="Peripheral \nROIs") --> -->

<!-- <!--       main <- str_match(type, "percent_(.*)_total")[,2] --> -->
<!-- <!--       gridExtra::grid.arrange(p1, p2, ncol = 2, --> -->
<!-- <!--                               top = "% of Cells Present in", --> -->
<!-- <!--                               left =  paste("Overall", main, "immune cells (%) per patients"), --> -->
<!-- <!--                               bottom = "Data on Race-Matched Patients") --> -->
<!-- <!--     } --> -->
<!-- <!--   } --> -->
<!-- <!-- } --> -->
<!-- <!-- ``` --> -->

<!-- <!-- #### CD3 --> -->
<!-- <!-- ```{r} --> -->
<!-- <!-- violin_plot(data = markers, type = "percent_CD3_total") --> -->
<!-- <!-- ``` --> -->

<!-- <!-- #### CD3 CD8 --> -->
<!-- <!-- ```{r} --> -->
<!-- <!-- violin_plot(data = markers, type = "percent_CD3_CD8_total") --> -->
<!-- <!-- ``` --> -->

<!-- <!-- #### CD3 FoxP3 --> -->
<!-- <!-- ```{r} --> -->
<!-- <!-- violin_plot(data = markers, type = "percent_CD3_FoxP3_total") --> -->
<!-- <!-- ``` --> -->

<!-- <!-- #### C11b --> -->
<!-- <!-- ```{r} --> -->
<!-- <!-- violin_plot(data = markers, type = "percent_CD11b_total") --> -->
<!-- <!-- ``` --> -->

<!-- <!-- #### CD11b CD15 --> -->
<!-- <!-- ```{r} --> -->
<!-- <!-- violin_plot(data = markers, type = "percent_CD11b_CD15_total") --> -->
<!-- <!-- ``` --> -->

<!-- <!-- ### Scatter plots --> -->
<!-- <!-- ```{r point} --> -->
<!-- <!-- point_plot <- function(data, type){ --> -->

<!-- <!--   for (i in exposure_var){ --> -->

<!-- <!--     if(class(markers[[i]]) == "numeric" | class(markers[[i]]) == "integer") { --> -->

<!-- <!--       p1 <- markers %>% --> -->
<!-- <!--         ggplot(aes(x=.data[[i]], y= .data[[paste0(type, ".i")]]))+ --> -->
<!-- <!--         geom_point()+ --> -->
<!-- <!--         geom_smooth(method = "lm", se = FALSE)+ --> -->
<!-- <!--         stat_regline_equation(label.y.npc = 1)+ --> -->
<!-- <!--         theme_classic()+ --> -->
<!-- <!--         labs(y=NULL, title="Intratumoral \nROIs") --> -->
<!-- <!--       p2 <- markers %>% --> -->
<!-- <!--         ggplot(aes(x=.data[[i]], y= .data[[paste0(type, ".p")]]))+ --> -->
<!-- <!--         geom_point()+ --> -->
<!-- <!--         geom_smooth(method = "lm", se = FALSE)+ --> -->
<!-- <!--         stat_regline_equation(label.y.npc = 1)+ --> -->
<!-- <!--         theme_classic()+ --> -->
<!-- <!--         labs(y=NULL, title="Peripheral \nROIs") --> -->

<!-- <!--       main <- str_match(type, "percent_(.*)_total")[,2] %>% --> -->
<!-- <!--         str_remove(., "_") --> -->
<!-- <!--       gridExtra::grid.arrange(p1, p2, ncol = 2, --> -->
<!-- <!--                               top = "% of Cells Present in", --> -->
<!-- <!--                               left =  paste("Overall", main, "immune cells (%) per patients"), --> -->
<!-- <!--                               bottom = "Data on Race-Matched Patients") --> -->
<!-- <!--     } --> -->
<!-- <!--   } --> -->
<!-- <!-- } --> -->
<!-- <!-- ``` --> -->

<!-- <!-- #### CD3 --> -->
<!-- <!-- ```{r} --> -->
<!-- <!-- point_plot(data = markers, type = "percent_CD3_total") --> -->
<!-- <!-- ``` --> -->

<!-- <!-- #### CD3 CD8 --> -->
<!-- <!-- ```{r} --> -->
<!-- <!-- point_plot(data = markers, type = "percent_CD3_CD8_total") --> -->
<!-- <!-- ``` --> -->

<!-- <!-- #### CD3 FoxP3 --> -->
<!-- <!-- ```{r} --> -->
<!-- <!-- point_plot(data = markers, type = "percent_CD3_FoxP3_total") --> -->
<!-- <!-- ``` --> -->

<!-- <!-- #### CD11b --> -->
<!-- <!-- ```{r} --> -->
<!-- <!-- point_plot(data = markers, type = "percent_CD11b_total") --> -->
<!-- <!-- ``` --> -->

<!-- <!-- #### CD11b CD15 --> -->
<!-- <!-- ```{r} --> -->
<!-- <!-- point_plot(data = markers, type = "percent_CD11b_CD15_total") --> -->
<!-- <!-- ``` --> -->
<!-- <br> -->
<!-- <br> -->

<!-- *** -->
<!-- *** -->

<!-- <br> -->

# II. Risk assessement adjusted by age + site
I created the dummy variables.
```{r dummy}
ctrl_case <- markers %>%
  filter(casecon == "Control" | !is.na(mean_tumor.i)) %>%
  mutate_at(c("CD3_tumor.i", "CD3_total.i", "CD3_stroma.i",
              "CD3_CD8_tumor.i", "CD3_CD8_total.i", "CD3_CD8_stroma.i"),
            ~ case_when(
              casecon == "Control"                                   ~ 0,
              . == "low"                                             ~ 1,
              . == "high"                                            ~ 2,
              is.na(.) ~ NA_real_
            )) %>%
  mutate_at(c("CD11b_tumor.i", "CD11b_total.i", "CD11b_stroma.i",
              "CD11b_CD15_tumor.i", "CD11b_CD15_total.i", "CD11b_CD15_stroma.i"),
            ~ case_when(
              casecon == "Control"                                   ~ 0,
              . == "Absence"                                         ~ 1,
              . == "Presence"                                        ~ 2,
            )) %>%
  mutate_at(c("immunoscore_2018lancet_patients"),
            ~ case_when(
              casecon == "Control"                                   ~ 0,
              . == "Low"                                             ~ 1,
              . == "Intermediate"                                    ~ 2,
              . == "High"                                            ~ 3
            ))

ctrl_case <- dummy_cols(ctrl_case,
                        select_columns =
                          c("BMI_recent_grp", "BMI_YA_grp",
                            "smokcurrent",
                            "packyrs_cat",
                            "tertile_loc",
                            "tertile_diidensity"
                            ))
table(ctrl_case$casecon)
table(ctrl_case$slide_type_considered)
colnames(ctrl_case)
```

## 2 levels factor variable
```{r 2 levels factor variable}
factor_name <- c("smokever",
                 "endomet", "pid", "fibroids",
                 "talcever", "talcgen", "talcnongen",
                 "diab", "hrtdis", "hbp", "hchol",
                 "aspirin", "NSAID", "aceta",
                 "inactive", "paga",
                 "education",
                 "diidensity", "diidenswithsupp",
                 "famhist_br_ov",
                 "perceived_discrim", "phys_trust",
                 "BMI_YA_2grp")

risk_ass <- function(data, type){

  for (i in factor_name){

    print(paste("RISK ASSESSMENT FOR ->", i, ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", i),
                data = data)

    print(risk[["or_ci_p"]])

  }
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
Exclude patients with no stroma data
```{r}
ctrl_case_stroma <- ctrl_case %>% 
  filter(casecon == "Control" | !is.na(CD3_stroma.i))

table(ctrl_case_stroma$casecon)
table(ctrl_case_stroma$slide_type_considered)

risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
ctrl_case_imm <- ctrl_case %>% 
  filter(casecon == "Control" | !is.na(immunoscore_2018lancet_patients))

table(ctrl_case_imm$casecon)
table(ctrl_case_imm$slide_type_considered)

risk_ass <- function(data, type){

  for (i in factor_name){

    print(paste("RISK ASSESSMENT FOR ->", i, ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", i),
                data = data)

    print(risk[["or_ci_p"]])

  }
}

risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```

## 3 levels factor variable - smokcurrent
```{r 3 levels factor variable - smokcurrent}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "smokcurrent_current", "smokcurrent_former"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "smokcurrent",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
table(ctrl_case$casecon)
table(ctrl_case$slide_type_considered)

risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "smokcurrent_current", "smokcurrent_former"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "smokcurrent",
                        nlevels = 3))
}
risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```

## 3 levels factor variable - packyrs_cat
```{r 3 levels factor variable - packyrs_cat}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "packyrs_cat", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "packyrs_cat",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "packyrs_cat", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "packyrs_cat",
                        nlevels = 3))
}
risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - tertile_loc
```{r 3 levels factor variable - tertile_loc}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_loc_Medium", "tertile_loc_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "tertile_loc_Medium", "tertile_loc_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_loc", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_loc",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_loc_Medium", "tertile_loc_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "tertile_loc_Medium", "tertile_loc_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_loc", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_loc",
                        nlevels = 3))
}
risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - tertile_diidensity
```{r 3 levels factor variable - tertile_diidensity}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_diidensity_Medium", "tertile_diidensity_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "tertile_diidensity_Medium", "tertile_diidensity_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_diidensity", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_diidensity",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_diidensity_Medium", "tertile_diidensity_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "tertile_diidensity_Medium", "tertile_diidensity_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_diidensity", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_diidensity",
                        nlevels = 3))
}
risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - BMI_recent_grp
```{r 3 levels factor variable - BMI_recent_grp}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_recent_grp",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_recent_grp",
                        nlevels = 3))
}
risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - BMI_YA_grp
```{r 3 levels factor variable - BMI_YA_grp}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_YA_grp",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
table(ctrl_case$casecon)
table(ctrl_case$slide_type_considered)

risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
table(ctrl_case_stroma$casecon)
table(ctrl_case_stroma$slide_type_considered)

risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_YA_grp",
                        nlevels = 3))
}
table(ctrl_case_imm$casecon)
table(ctrl_case_imm$slide_type_considered)

risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

***

# III. Secondary analysis - Case only

```{r}
markers_cases <- markers %>%
  filter(casecon == "Case")
```

## 1.Distribution
```{r distribution, fig.height=12, fig.width=12}
markers_cases %>%
  select(starts_with("percent_CD3"), starts_with("percent_CD11b")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(region = case_when(
    str_detect(name, ".i")           ~ "intratumoral",
    str_detect(name, ".p")           ~ "peripheral",
    str_detect(name, "_tma")         ~ "TMA",
  )) %>%
  mutate(compartment = case_when(
    str_detect(name, "tumor")           ~ "tumor",
    str_detect(name, "stroma")           ~ "stroma",
    str_detect(name, "total")           ~ "total"
  )) %>%
  mutate(marker = str_match(name, "percent_(.*)(_total|_tumor|_stroma)")[,2]) %>%
  ggplot(aes(value, color= compartment, fill= compartment))+
  geom_density(alpha=.5)+
  theme_classic()+
  facet_wrap(region ~ marker, scales = "free", nrow = 3) +
  theme(legend.position="bottom")
```

## 2.Logistic regression on category variables adjusted by age + site
Results are exponentiated.

### 2 categories var
```{r log reg function}
loreg_table_int <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_remove(., "_")

    tbl1 <- glm(data[[paste0(type, ".i")]] ~ data[[i]] + refage + site,
                data = data, family = "binomial") %>%
            tbl_regression(exponentiate = TRUE,
                           intercept = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Intratumoral"))
    print(tbl1)

  }
}

loreg_table_per <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_remove(., "_")

    tbl2 <- glm(data[[paste0(type, ".p")]] ~ data[[i]] + refage + site,
                data = data, family = "binomial") %>%
            tbl_regression(exponentiate = TRUE,
                           intercept = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Peripheral"))
    print(tbl2)

  }
}
```

#### CD3_total

<div class = "row">
<div class = "col-md-6">
```{r log reg intra, results = 'asis'}
loreg_table_int(data = markers_cases, type = "CD3_total")
```
</div>

<div class = "col-md-6">
```{r log reg periph, results = 'asis'}
# loreg_table_per(data = markers_cases, type = "CD3_total")
```
</div>
</div>

***

#### CD3_CD8_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_cases, type = "CD3_CD8_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_cases, type = "CD3_CD8_total")
```
</div>
</div>

***

#### CD3_FoxP3_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_cases, type = "CD3_FoxP3_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_cases, type = "CD3_FoxP3_total")
```
</div>
</div>

***

#### CD11b_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_cases, type = "CD11b_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_cases, type = "CD11b_total")
```
</div>
</div>

***

#### CD11b_CD15_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_cases, type = "CD11b_CD15_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_cases, type = "CD11b_CD15_total")
```
</div>
</div>

<br>

***
***

<br>

### Immunoscore 3 cat 2018-lancet

What are the weight? Example: model immunoscore with BMI + age + site
```{r}
multinom(immunoscore_2018lancet_patients ~ BMI_recent_grp + refage + site,
                     data = markers_cases)
```

```{r multi reg function}
multinom_pivot_wider <- function(x) {
  # check inputs match expectatations
  if (!inherits(x, "tbl_regression") || !inherits(x$model_obj, "multinom")) {
    stop("`x=` must be class 'tbl_regression' summary of a `nnet::multinom()` model.")
  }

  # create tibble of results
  df <- tibble::tibble(outcome_level = unique(x$table_body$groupname_col))
  df$tbl <-
    purrr::map(
      df$outcome_level,
      function(lvl) {
        gtsummary::modify_table_body(
          x,
          ~dplyr::filter(.x, .data$groupname_col %in% lvl) %>%
            dplyr::ungroup() %>%
            dplyr::select(-.data$groupname_col)
        )
      }
    )

  tbl_merge(df$tbl, tab_spanner = paste0("**", df$outcome_level, "**"))
}

multireg_table <- function(data){

  for (i in exposure_var){

    tbl1 <- multinom(immunoscore_2018lancet_patients ~ data[[i]] + refage + site,
                     data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
  multinom_pivot_wider() #%>%
            # modify_spanning_header(everything() ~ paste("Association with Overall", "immunoscore_patients", "Intratumoral"))
    print(tbl1)

  }
}
```

```{r reg immunoscore age and site, results = 'asis'}
multireg_table(data = markers_cases)
```
<br>

***
***

<br>
<br>

# 3. Logistic regression on Continuous variables adjusted by age + site

```{r glm function}
glm_table_int <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_replace(., "_", " ")

    tbl1 <- glm(data[[paste0(type, ".i")]] ~ data[[i]] + refage + site,
                data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Intratumoral"))
    print(tbl1)

  }
}

glm_table_per <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_replace(., "_", " ")

    tbl1 <- glm(data[[paste0(type, ".p")]] ~ data[[i]] + refage + site,
                data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Peripheral"))
    print(tbl1)

  }
}
```

## CD3_total

<div class = "row">
<div class = "col-md-6">
```{r glm intra, results = 'asis'}
glm_table_int(data = markers_cases, type = "percent_CD3_total")
```
</div>

<div class = "col-md-6">
```{r glm periph, results = 'asis'}
# glm_table_per(data = markers_cases, type = "percent_CD3_total")
```
</div>
</div>

***

## CD3_CD8_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_cases, type = "percent_CD3_CD8_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# glm_table_per(data = markers_cases, type = "percent_CD3_CD8_total")
```
</div>
</div>

***

## CD3_FoxP3_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_cases, type = "percent_CD3_FoxP3_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# glm_table_per(data = markers_cases, type = "percent_CD3_FoxP3_total")
```
</div>
</div>

***

## CD11b_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_cases, type = "percent_CD11b_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# glm_table_per(data = markers_cases, type = "percent_CD11b_total")
```
</div>
</div>

***

## CD11b_CD15_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_cases, type = "percent_CD11b_CD15_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# glm_table_per(data = markers_cases, type = "percent_CD11b_CD15_total")
```
</div>
</div>

<br>

***
***

# Include TMA as intratumoral ROI

```{r add TMA to data}
markers_wTMA <- markers %>% 
  mutate(CD3_total.i = coalesce(CD3_total.i, CD3_total_tma),
         CD3_CD8_total.i = coalesce(CD3_CD8_total.i, CD3_CD8_total_tma),
         CD3_FoxP3_total.i = coalesce(CD3_FoxP3_total.i, CD3_FoxP3_total_tma),
         CD11b_total.i = coalesce(CD11b_total.i, CD11b_total_tma),
         CD11b_CD15_total.i = coalesce(CD11b_CD15_total.i, CD11b_CD15_total_tma),
         
         CD3_tumor.i = coalesce(CD3_tumor.i, CD3_tumor_tma),
         CD3_CD8_tumor.i = coalesce(CD3_CD8_tumor.i, CD3_CD8_tumor_tma),
         CD3_FoxP3_tumor.i = coalesce(CD3_FoxP3_tumor.i, CD3_FoxP3_tumor_tma),
         CD11b_tumor.i = coalesce(CD11b_tumor.i, CD11b_tumor_tma),
         CD11b_CD15_tumor.i = coalesce(CD11b_CD15_tumor.i, CD11b_CD15_tumor_tma),
         
         CD3_stroma.i = coalesce(CD3_stroma.i, CD3_stroma_tma),
         CD3_CD8_stroma.i = coalesce(CD3_CD8_stroma.i, CD3_CD8_stroma_tma),
         CD3_FoxP3_stroma.i = coalesce(CD3_FoxP3_stroma.i, CD3_FoxP3_stroma_tma),
         CD11b_stroma.i = coalesce(CD11b_stroma.i, CD11b_stroma_tma),
         CD11b_CD15_stroma.i = coalesce(CD11b_CD15_stroma.i, CD11b_CD15_stroma_tma),
         
         percent_CD3_total.i = coalesce(percent_CD3_total.i, percent_CD3_total_tma),
         percent_CD3_CD8_total.i = coalesce(percent_CD3_CD8_total.i, percent_CD3_CD8_total_tma),
         percent_CD3_FoxP3_total.i = coalesce(percent_CD3_FoxP3_total.i, percent_CD3_FoxP3_total_tma),
         percent_CD11b_total.i = coalesce(percent_CD11b_total.i, percent_CD11b_total_tma),
         percent_CD11b_CD15_total.i = coalesce(percent_CD11b_CD15_total.i, percent_CD11b_CD15_total_tma),
         
         percent_CD3_tumor.i = coalesce(percent_CD3_tumor.i, percent_CD3_tumor_tma),
         percent_CD3_CD8_tumor.i = coalesce(percent_CD3_CD8_tumor.i, percent_CD3_CD8_tumor_tma),
         percent_CD3_FoxP3_tumor.i = coalesce(percent_CD3_FoxP3_tumor.i, percent_CD3_FoxP3_tumor_tma),
         percent_CD11b_tumor.i = coalesce(percent_CD11b_tumor.i, percent_CD11b_tumor_tma),
         percent_CD11b_CD15_tumor.i = coalesce(percent_CD11b_CD15_tumor.i, percent_CD11b_CD15_tumor_tma),
         
         percent_CD3_stroma.i = coalesce(percent_CD3_stroma.i, percent_CD3_stroma_tma),
         percent_CD3_CD8_stroma.i = coalesce(percent_CD3_CD8_stroma.i, percent_CD3_CD8_stroma_tma),
         percent_CD3_FoxP3_stroma.i = coalesce(percent_CD3_FoxP3_stroma.i, percent_CD3_FoxP3_stroma_tma),
         percent_CD11b_stroma.i = coalesce(percent_CD11b_stroma.i, percent_CD11b_stroma_tma),
         percent_CD11b_CD15_stroma.i = coalesce(percent_CD11b_CD15_stroma.i, percent_CD11b_CD15_stroma_tma),
         
         mean_tumor_tma = mean_tumor_tma / 100,
         mean_tumor.i = mean_tumor.i / 100,
         prop_tumor = coalesce(prop_tumor, mean_tumor_tma)
         )
```

```{r}
markers_wTMA %>%
  select(mean_tumor.i, mean_tumor_tma) %>%
  pivot_longer(cols = c(mean_tumor.i, mean_tumor_tma)) %>%
  filter(!is.na(value)) %>%
  ggplot(aes(x= name, y= value))+
  geom_boxplot()
```

## Updated 4. Immune characteristics (Cases) combining intratumoral + tma
```{r Immune tableb}
markers_wTMA %>%
  filter(casecon == "Case") %>%
  select(starts_with("CD"), -c(ends_with("_tma")), -c(ends_with(".p"))) %>%
  tbl_summary(
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)) %>%
      # modify_header(list(label ~ "**Patient characteristics**", all_stat_cols() ~ "**{level}**, N = {n}")) %>%
  bold_labels()
```
Instead of 2 missing in stroma, here only one bc filled up by a TMA.

# IIb. Risk assessement adjusted by age + site + average proportion tumor
```{r dummyb}
ctrl_case <- markers_wTMA %>% 
  filter(casecon == "Control" | !is.na(prop_tumor)) %>% # No need to care about cases who only has intra or peri.
  # They are automatically  excluded when running the function.
  mutate_at(c("CD3_tumor.i", "CD3_total.i", "CD3_stroma.i",
              "CD3_CD8_tumor.i", "CD3_CD8_total.i", "CD3_CD8_stroma.i"),
            ~ case_when(
              casecon == "Control"                                   ~ 0,
              . == "low"                                             ~ 1,
              . == "high"                                            ~ 2
            )) %>%
  mutate_at(c("CD11b_tumor.i", "CD11b_total.i", "CD11b_stroma.i",
              "CD11b_CD15_tumor.i", "CD11b_CD15_total.i", "CD11b_CD15_stroma.i"),
            ~ case_when(
              casecon == "Control"                                   ~ 0,
              . == "Absence"                                         ~ 1,
              . == "Presence"                                        ~ 2
            )) %>% 
  mutate(immunoscore_2018lancet_patients = case_when(
    casecon == "Control"                                             ~ 0,
    immunoscore_2018lancet_patients == "Low"                         ~ 1,
    immunoscore_2018lancet_patients == "Intermediate"                ~ 2,
    immunoscore_2018lancet_patients == "High"                        ~ 3
  ))

ctrl_case <- dummy_cols(ctrl_case,
                        select_columns =
                          c("BMI_recent_grp", "BMI_YA_grp",
                            "smokcurrent",
                            "packyrs_cat",
                            "tertile_loc",
                            "tertile_diidensity"
                            ))
table(ctrl_case$casecon)
table(ctrl_case$slide_type_considered)
```

## 2 levels factor variable
```{r 2 levels factor variableb}
factor_name <- c("smokever",
                 "endomet", "pid", "fibroids",
                 "talcever", "talcgen", "talcnongen",
                 "diab", "hrtdis", "hbp", "hchol",
                 "aspirin", "NSAID", "aceta",
                 "inactive", "paga",
                 "education",
                 "diidensity", "diidenswithsupp",
                 "famhist_br_ov",
                 "perceived_discrim", "phys_trust",
                 "BMI_YA_2grp")

risk_ass <- function(data, type){

  for (i in factor_name){

    print(paste("RISK ASSESSMENT FOR ->", i, ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "prop_tumor", i),
                data = data)

    print(risk[["or_ci_p"]])

  }
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
Exclude patients with no stroma data
```{r}
ctrl_case_stroma <- ctrl_case %>% 
  filter(casecon == "Control" | !is.na(CD3_stroma.i))

table(ctrl_case_stroma$casecon)
table(ctrl_case_stroma$slide_type_considered)

risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls - Excluding missing peripheral**
```{r}
# ctrl_case_imm <- ctrl_case %>% 
#   filter(casecon == "Control" | !is.na(immunoscore_2018lancet_patients))
# 
# table(ctrl_case_imm$casecon)
# table(ctrl_case_imm$slide_type_considered)
# 
# risk_ass <- function(data, type){
# 
#   for (i in factor_name){
# 
#     print(paste("RISK ASSESSMENT FOR ->", i, ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "prop_tumor", i),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#   }
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>

## 3 levels factor variable - smokcurrent
```{r 3 levels factor variable - smokcurrentb}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "prop_tumor", "smokcurrent_current", "smokcurrent_former"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "smokcurrent",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
table(ctrl_case$casecon)
table(ctrl_case$slide_type_considered)

risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
table(ctrl_case_stroma$casecon)
table(ctrl_case_stroma$slide_type_considered)

risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "prop_tumor", "smokcurrent_current", "smokcurrent_former"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "smokcurrent",
#                         nlevels = 3))
# }
# 
# table(ctrl_case_imm$casecon)
# table(ctrl_case_imm$slide_type_considered)
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>

## 3 levels factor variable - packyrs_cat
```{r 3 levels factor variable - packyrs_catb}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "prop_tumor", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "packyrs_cat", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "packyrs_cat",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "prop_tumor", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "packyrs_cat", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "packyrs_cat",
#                         nlevels = 3))
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>

## 3 levels factor variable - tertile_loc
```{r 3 levels factor variable - tertile_locb}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_loc_Medium", "tertile_loc_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "prop_tumor", "tertile_loc_Medium", "tertile_loc_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_loc", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_loc",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "tertile_loc_Medium", "tertile_loc_High", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "prop_tumor", "tertile_loc_Medium", "tertile_loc_High"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "tertile_loc", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "tertile_loc",
#                         nlevels = 3))
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>

## 3 levels factor variable - tertile_diidensity
```{r 3 levels factor variable - tertile_diidensityb}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_diidensity_Medium", "tertile_diidensity_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "prop_tumor", "tertile_diidensity_Medium", "tertile_diidensity_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_diidensity", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_diidensity",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "tertile_diidensity_Medium", "tertile_diidensity_High", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "prop_tumor", "tertile_diidensity_Medium", "tertile_diidensity_High"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "tertile_diidensity", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "tertile_diidensity",
#                         nlevels = 3))
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>

## 3 levels factor variable - BMI_recent_grp
```{r 3 levels factor variable - BMI_recent_grpb}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "prop_tumor", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_recent_grp",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "prop_tumor", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "BMI_recent_grp",
#                         nlevels = 3))
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>

## 3 levels factor variable - BMI_YA_grp
```{r 3 levels factor variable - BMI_YA_grpb}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "prop_tumor", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_YA_grp",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "prop_tumor", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "BMI_YA_grp",
#                         nlevels = 3))
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>

***

# IIIb. Secondary analysis - Case only

```{r}
markers_wTMA_cases <- markers_wTMA %>%
  filter(casecon == "Case")
```

## 1.Distribution
Use plot from before unless we want an updated distribution with values of intratumoral + TMA combined
```{r}

```

## 2b.Logistic regression on category variables adjusted by age + site
Results are exponentiated.

### 2 categories var
The regression on peripheral immune markers will not change when adding the TMA as we added TMA as intratumoral region.
```{r log reg functionb}
loreg_table_int <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_remove(., "_")

    tbl1 <- glm(data[[paste0(type, ".i")]] ~ data[[i]] + refage + site,
                data = data, family = "binomial") %>%
            tbl_regression(exponentiate = TRUE,
                           intercept = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Intratumoral"))
    print(tbl1)

  }
}
```

#### CD3_total

<div class = "row">
<div class = "col-md-6">
```{r log reg intra d, results = 'asis'}
loreg_table_int(data = markers_wTMA_cases, type = "CD3_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

#### CD3_CD8_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_wTMA_cases, type = "CD3_CD8_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

#### CD3_FoxP3_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_wTMA_cases, type = "CD3_FoxP3_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

#### CD11b_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_wTMA_cases, type = "CD11b_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

#### CD11b_CD15_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_wTMA_cases, type = "CD11b_CD15_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

<br>

***
***

<br>

### Immunoscore 3 cat 2018-lancet
TMA cannot be included in the immunoscore categories aka take previous values on ROI only.   
<br>

***
***

<br>
<br>

# 3b. Logistic regression on Continuous variables adjusted by age + site
The regression on peripheral immune markers will not change when adding the TMA as we added TMA as intratumoral region.
```{r glm functionb}
glm_table_int <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_replace(., "_", " ")

    tbl1 <- glm(data[[paste0(type, ".i")]] ~ data[[i]] + refage + site,
                data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Intratumoral"))
    print(tbl1)

  }
}
```

## CD3_total

<div class = "row">
<div class = "col-md-6">
```{r glm intrab, results = 'asis'}
glm_table_int(data = markers_wTMA_cases, type = "percent_CD3_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

## CD3_CD8_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_wTMA_cases, type = "percent_CD3_CD8_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

## CD3_FoxP3_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_wTMA_cases, type = "percent_CD3_FoxP3_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

## CD11b_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_wTMA_cases, type = "percent_CD11b_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

## CD11b_CD15_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_wTMA_cases, type = "percent_CD11b_CD15_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>
<br>
<br>

***
***

<br>
<br>

<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Fully adjusted models + fullpregnum + ocdur + tubelig + famhist_br_ov</span>

</div>

<br>

# Fully adjusted models age + site + fullpregnum + ocdur + tubelig + famhist_br_ov

# IV. Risk assessement
I created the dummy variables.
```{r dummyc}
ctrl_case <- markers %>%
  filter(casecon == "Control" | !is.na(mean_tumor.i)) %>% 
  mutate_at(c("CD3_tumor.i", "CD3_total.i", "CD3_stroma.i",
              "CD3_CD8_tumor.i", "CD3_CD8_total.i", "CD3_CD8_stroma.i"),
            ~ case_when(
              casecon == "Control"                                   ~ 0,
              . == "low"                                             ~ 1,
              . == "high"                                            ~ 2,
            )) %>%
  mutate_at(c("CD11b_tumor.i", "CD11b_total.i", "CD11b_stroma.i",
              "CD11b_CD15_tumor.i", "CD11b_CD15_total.i", "CD11b_CD15_stroma.i"),
            ~ case_when(
              casecon == "Control"                                   ~ 0,
              . == "Absence"                                         ~ 1,
              . == "Presence"                                        ~ 2,
            )) %>%
  mutate_at(c("immunoscore_2018lancet_patients"),
            ~ case_when(
              casecon == "Control"                                   ~ 0,
              . == "Low"                                             ~ 1,
              . == "Intermediate"                                    ~ 2,
              . == "High"                                            ~ 3
            ))

ctrl_case <- dummy_cols(ctrl_case,
                        select_columns =
                          c("BMI_recent_grp", "BMI_YA_grp",
                            "smokcurrent",
                            "packyrs_cat",
                            "tertile_loc",
                            "tertile_diidensity"
                            ))
table(ctrl_case$casecon)
table(ctrl_case$slide_type_considered)
```

## 2 levels factor variable
```{r 2 levels factor variable c}
factor_name <- c("smokever",
                 "endomet", "pid", "fibroids",
                 "talcever", "talcgen", "talcnongen",
                 "diab", "hrtdis", "hbp", "hchol",
                 "aspirin", "NSAID", "aceta",
                 "inactive", "paga",
                 "education",
                 "diidensity", "diidenswithsupp",
                 # "famhist_br_ov",
                 "perceived_discrim", "phys_trust",
                 "BMI_YA_2grp")

risk_ass <- function(data, type){

  for (i in factor_name){

    print(paste("RISK ASSESSMENT FOR ->", i, ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", i),
                data = data)

    print(risk[["or_ci_p"]])

  }
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
Exclude patients with no stroma data
```{r}
ctrl_case_stroma <- ctrl_case %>% 
  filter(casecon == "Control" | !is.na(CD3_stroma.i))

table(ctrl_case_stroma$casecon)
table(ctrl_case_stroma$slide_type_considered)

risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls - Excluding missing peripheral**
```{r}
ctrl_case_imm <- ctrl_case %>% 
  filter(casecon == "Control" | !is.na(immunoscore_2018lancet_patients))

table(ctrl_case_imm$casecon)
table(ctrl_case_imm$slide_type_considered)

risk_ass <- function(data, type){

  for (i in factor_name){

    print(paste("RISK ASSESSMENT FOR ->", i, ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", i),
                data = data)

    print(risk[["or_ci_p"]])

  }
}

risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```

## 3 levels factor variable - smokcurrent
```{r 3 levels factor variable - smokcurrent c}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "smokcurrent_current", "smokcurrent_former"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "smokcurrent",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
table(ctrl_case$casecon)
table(ctrl_case$slide_type_considered)

risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
table(ctrl_case$casecon)
table(ctrl_case$slide_type_considered)

risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "smokcurrent_current", "smokcurrent_former"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "smokcurrent",
                        nlevels = 3))
}
table(ctrl_case$casecon)
table(ctrl_case$slide_type_considered)

risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```

## 3 levels factor variable - packyrs_cat
```{r 3 levels factor variable - packyrs_cat c}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "packyrs_cat", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "packyrs_cat",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "packyrs_cat", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "packyrs_cat",
                        nlevels = 3))
}
risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - tertile_loc
```{r 3 levels factor variable - tertile_loc c}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_loc_Medium", "tertile_loc_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "tertile_loc_Medium", "tertile_loc_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_loc", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_loc",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_loc_Medium", "tertile_loc_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "tertile_loc_Medium", "tertile_loc_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_loc", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_loc",
                        nlevels = 3))
}
risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - tertile_diidensity
```{r 3 levels factor variable - tertile_diidensity c}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_diidensity_Medium", "tertile_diidensity_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "tertile_diidensity_Medium", "tertile_diidensity_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_diidensity", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_diidensity",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_diidensity_Medium", "tertile_diidensity_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "tertile_diidensity_Medium", "tertile_diidensity_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_diidensity", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_diidensity",
                        nlevels = 3))
}
risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - BMI_recent_grp
```{r 3 levels factor variable - BMI_recent_grp c}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_recent_grp",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_recent_grp",
                        nlevels = 3))
}
risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - BMI_YA_grp
```{r 3 levels factor variable - BMI_YA_grp c}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_YA_grp",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
**On data with ROI cases and controls**
```{r}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25", ":"))
    risk <- eh_test_subtype(label = type,
                M = 3,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_YA_grp",
                        nlevels = 3))
}
risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

***

# VI. Secondary analysis - Case only

```{r}
markers_cases <- markers %>%
  filter(casecon == "Case")
```

## 1.Distribution
Same as before
```{r}

```

## 2.Logistic regression on category variables adjusted by age + site + fullpregnum + ocdur + tubelig+ famhist_br_ov
Results are exponentiated.

### 2 categories var
```{r log reg function c}
loreg_table_int <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_remove(., "_")

    tbl1 <- glm(data[[paste0(type, ".i")]] ~ data[[i]] + refage + site + fullpregnum + ocdur + tubelig+ famhist_br_ov,
                data = data, family = "binomial") %>%
            tbl_regression(exponentiate = TRUE,
                           intercept = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Intratumoral"))
    print(tbl1)

  }
}

loreg_table_per <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_remove(., "_")

    tbl2 <- glm(data[[paste0(type, ".p")]] ~ data[[i]] + refage + site + fullpregnum + ocdur + tubelig+ famhist_br_ov,
                data = data, family = "binomial") %>%
            tbl_regression(exponentiate = TRUE,
                           intercept = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Peripheral"))
    print(tbl2)

  }
}
```

#### CD3_total

<div class = "row">
<div class = "col-md-6">
```{r log reg intra c, results = 'asis'}
loreg_table_int(data = markers_cases, type = "CD3_total")
```
</div>

<div class = "col-md-6">
```{r log reg periph c, results = 'asis'}
# loreg_table_per(data = markers_cases, type = "CD3_total")
```
</div>
</div>

***

#### CD3_CD8_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_cases, type = "CD3_CD8_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_cases, type = "CD3_CD8_total")
```
</div>
</div>

***

#### CD3_FoxP3_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_cases, type = "CD3_FoxP3_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_cases, type = "CD3_FoxP3_total")
```
</div>
</div>

***

#### CD11b_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_cases, type = "CD11b_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_cases, type = "CD11b_total")
```
</div>
</div>

***

#### CD11b_CD15_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_cases, type = "CD11b_CD15_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_cases, type = "CD11b_CD15_total")
```
</div>
</div>

<br>

***
***

<br>

### Immunoscore 3 cat 2018-lancet

```{r reg immunoscore fully adjusted function}
multinom_pivot_wider <- function(x) {
  # check inputs match expectatations
  if (!inherits(x, "tbl_regression") || !inherits(x$model_obj, "multinom")) {
    stop("`x=` must be class 'tbl_regression' summary of a `nnet::multinom()` model.")
  }

  # create tibble of results
  df <- tibble::tibble(outcome_level = unique(x$table_body$groupname_col))
  df$tbl <-
    purrr::map(
      df$outcome_level,
      function(lvl) {
        gtsummary::modify_table_body(
          x,
          ~dplyr::filter(.x, .data$groupname_col %in% lvl) %>%
            dplyr::ungroup() %>%
            dplyr::select(-.data$groupname_col)
        )
      }
    )

  tbl_merge(df$tbl, tab_spanner = paste0("**", df$outcome_level, "**"))
}

multireg_table <- function(data){

  for (i in exposure_var){

    tbl1 <- multinom(immunoscore_2018lancet_patients ~ data[[i]] + refage + site + fullpregnum + ocdur + tubelig+ famhist_br_ov,
                     data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
  multinom_pivot_wider() #%>%
            # modify_spanning_header(everything() ~ paste("Association with Overall", "immunoscore_patients", "Intratumoral"))
    print(tbl1)

  }
}
```

```{r, results = 'asis'}
multireg_table(data = markers_cases)
```
<br>

***
***

<br>
<br>

# 3. Logistic regression on Continuous variables adjusted by age + site

```{r glm function c}
glm_table_int <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_replace(., "_", " ")

    tbl1 <- glm(data[[paste0(type, ".i")]] ~ data[[i]] + refage + site + fullpregnum + ocdur + tubelig+ famhist_br_ov,
                data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Intratumoral"))
    print(tbl1)

  }
}

glm_table_per <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_replace(., "_", " ")

    tbl1 <- glm(data[[paste0(type, ".p")]] ~ data[[i]] + refage + site + fullpregnum + ocdur + tubelig+ famhist_br_ov,
                data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Peripheral"))
    print(tbl1)

  }
}
```

## CD3_total

<div class = "row">
<div class = "col-md-6">
```{r glm intra c, results = 'asis'}
glm_table_int(data = markers_cases, type = "percent_CD3_total")
```
</div>

<div class = "col-md-6">
```{r glm periph c, results = 'asis'}
# glm_table_per(data = markers_cases, type = "percent_CD3_total")
```
</div>
</div>

***

## CD3_CD8_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_cases, type = "percent_CD3_CD8_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# glm_table_per(data = markers_cases, type = "percent_CD3_CD8_total")
```
</div>
</div>

***

## CD3_FoxP3_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_cases, type = "percent_CD3_FoxP3_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# glm_table_per(data = markers_cases, type = "percent_CD3_FoxP3_total")
```
</div>
</div>

***

## CD11b_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_cases, type = "percent_CD11b_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# glm_table_per(data = markers_cases, type = "percent_CD11b_total")
```
</div>
</div>

***

## CD11b_CD15_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_cases, type = "percent_CD11b_CD15_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# glm_table_per(data = markers_cases, type = "percent_CD11b_CD15_total")
```
</div>
</div>

<br>

***
***

# Include TMA as intratumoral ROI

```{r add TMA to data for fully adjusted model}
markers_wTMA <- markers %>% 
  mutate(CD3_total.i = coalesce(CD3_total.i, CD3_total_tma),
         CD3_CD8_total.i = coalesce(CD3_CD8_total.i, CD3_CD8_total_tma),
         CD3_FoxP3_total.i = coalesce(CD3_FoxP3_total.i, CD3_FoxP3_total_tma),
         CD11b_total.i = coalesce(CD11b_total.i, CD11b_total_tma),
         CD11b_CD15_total.i = coalesce(CD11b_CD15_total.i, CD11b_CD15_total_tma),
         
         CD3_tumor.i = coalesce(CD3_tumor.i, CD3_tumor_tma),
         CD3_CD8_tumor.i = coalesce(CD3_CD8_tumor.i, CD3_CD8_tumor_tma),
         CD3_FoxP3_tumor.i = coalesce(CD3_FoxP3_tumor.i, CD3_FoxP3_tumor_tma),
         CD11b_tumor.i = coalesce(CD11b_tumor.i, CD11b_tumor_tma),
         CD11b_CD15_tumor.i = coalesce(CD11b_CD15_tumor.i, CD11b_CD15_tumor_tma),
         
         CD3_stroma.i = coalesce(CD3_stroma.i, CD3_stroma_tma),
         CD3_CD8_stroma.i = coalesce(CD3_CD8_stroma.i, CD3_CD8_stroma_tma),
         CD3_FoxP3_stroma.i = coalesce(CD3_FoxP3_stroma.i, CD3_FoxP3_stroma_tma),
         CD11b_stroma.i = coalesce(CD11b_stroma.i, CD11b_stroma_tma),
         CD11b_CD15_stroma.i = coalesce(CD11b_CD15_stroma.i, CD11b_CD15_stroma_tma),
         
         percent_CD3_total.i = coalesce(percent_CD3_total.i, percent_CD3_total_tma),
         percent_CD3_CD8_total.i = coalesce(percent_CD3_CD8_total.i, percent_CD3_CD8_total_tma),
         percent_CD3_FoxP3_total.i = coalesce(percent_CD3_FoxP3_total.i, percent_CD3_FoxP3_total_tma),
         percent_CD11b_total.i = coalesce(percent_CD11b_total.i, percent_CD11b_total_tma),
         percent_CD11b_CD15_total.i = coalesce(percent_CD11b_CD15_total.i, percent_CD11b_CD15_total_tma),
         
         percent_CD3_tumor.i = coalesce(percent_CD3_tumor.i, percent_CD3_tumor_tma),
         percent_CD3_CD8_tumor.i = coalesce(percent_CD3_CD8_tumor.i, percent_CD3_CD8_tumor_tma),
         percent_CD3_FoxP3_tumor.i = coalesce(percent_CD3_FoxP3_tumor.i, percent_CD3_FoxP3_tumor_tma),
         percent_CD11b_tumor.i = coalesce(percent_CD11b_tumor.i, percent_CD11b_tumor_tma),
         percent_CD11b_CD15_tumor.i = coalesce(percent_CD11b_CD15_tumor.i, percent_CD11b_CD15_tumor_tma),
         
         percent_CD3_stroma.i = coalesce(percent_CD3_stroma.i, percent_CD3_stroma_tma),
         percent_CD3_CD8_stroma.i = coalesce(percent_CD3_CD8_stroma.i, percent_CD3_CD8_stroma_tma),
         percent_CD3_FoxP3_stroma.i = coalesce(percent_CD3_FoxP3_stroma.i, percent_CD3_FoxP3_stroma_tma),
         percent_CD11b_stroma.i = coalesce(percent_CD11b_stroma.i, percent_CD11b_stroma_tma),
         percent_CD11b_CD15_stroma.i = coalesce(percent_CD11b_CD15_stroma.i, percent_CD11b_CD15_stroma_tma),
         
         mean_tumor_tma = mean_tumor_tma / 100,
         mean_tumor.i = mean_tumor.i / 100,
         prop_tumor = coalesce(prop_tumor, mean_tumor_tma)
         )
```

## Updated table 4. Immune characteristics (Cases) combining intratumoral + tma
Same as previous Updated table 4
```{r}
```

# Vb. Risk assessement adjusted by age + site + fullpregnum + ocdur + tubelig + famhist_br_ov + average proportion tumor 
```{r dummy d}
ctrl_case <- markers_wTMA %>% 
  filter(casecon == "Control" | !is.na(prop_tumor)) %>% # No need to care about cases who only has intra or peri.
  # They are automatically  excluded when running the function.
  mutate_at(c("CD3_tumor.i", "CD3_total.i", "CD3_stroma.i",
              "CD3_CD8_tumor.i", "CD3_CD8_total.i", "CD3_CD8_stroma.i"),
            ~ case_when(
              casecon == "Control"                                   ~ 0,
              . == "low"                                             ~ 1,
              . == "high"                                            ~ 2
            )) %>%
  mutate_at(c("CD11b_tumor.i", "CD11b_total.i", "CD11b_stroma.i",
              "CD11b_CD15_tumor.i", "CD11b_CD15_total.i", "CD11b_CD15_stroma.i"),
            ~ case_when(
              casecon == "Control"                                   ~ 0,
              . == "Absence"                                         ~ 1,
              . == "Presence"                                        ~ 2
            )) %>% 
  mutate(immunoscore_2018lancet_patients = case_when(
    casecon == "Control"                                   ~ 0,
    immunoscore_2018lancet_patients == "Low"                                             ~ 1,
    immunoscore_2018lancet_patients == "Intermediate"                                    ~ 2,
    immunoscore_2018lancet_patients == "High"                                            ~ 3
  ))

ctrl_case <- dummy_cols(ctrl_case,
                        select_columns =
                          c("BMI_recent_grp", "BMI_YA_grp",
                            "smokcurrent",
                            "packyrs_cat",
                            "tertile_loc",
                            "tertile_diidensity"
                            ))
table(ctrl_case$casecon)
table(ctrl_case$slide_type_considered)
```

## 2 levels factor variable
```{r 2 levels factor variable d}
factor_name <- c("smokever",
                 "endomet", "pid", "fibroids",
                 "talcever", "talcgen", "talcnongen",
                 "diab", "hrtdis", "hbp", "hchol",
                 "aspirin", "NSAID", "aceta",
                 "inactive", "paga",
                 "education",
                 "diidensity", "diidenswithsupp",
                 "famhist_br_ov",
                 "perceived_discrim", "phys_trust",
                 "BMI_YA_2grp")

risk_ass <- function(data, type){

  for (i in factor_name){
    
    print(paste("RISK ASSESSMENT FOR ->", i, ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", i),
                data = data)

    print(risk[["or_ci_p"]])

  }
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
Patients with no stroma data are excluded
```{r}
ctrl_case_stroma <- ctrl_case %>% 
  filter(casecon == "Control" | !is.na(CD3_stroma.i))

table(ctrl_case_stroma$casecon)
table(ctrl_case_stroma$slide_type_considered)
  
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
<!-- Exclude the 3 patients with no peripheral values -->
```{r}
# ctrl_case_imm <- ctrl_case %>% 
#   filter(casecon == "Control" | !is.na(immunoscore_2018lancet_patients))
# 
# table(ctrl_case_imm$casecon)
# table(ctrl_case_imm$slide_type_considered)
# 
# risk_ass <- function(data, type){
# 
#   for (i in factor_name){
#     
#     print(paste("RISK ASSESSMENT FOR ->", i, ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", i),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#   }
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>

## 3 levels factor variable - smokcurrent
```{r 3 levels factor variable - smokcurrent d}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "smokcurrent_current", "smokcurrent_former"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "smokcurrent",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "smokcurrent_current", "smokcurrent_former"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "smokcurrent",
#                         nlevels = 3))
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>

## 3 levels factor variable - packyrs_cat
```{r 3 levels factor variable - packyrs_cat d}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "packyrs_cat", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "packyrs_cat",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "packyrs_cat", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "packyrs_cat",
#                         nlevels = 3))
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - tertile_loc
```{r 3 levels factor variable - tertile_loc d}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_loc_Medium", "tertile_loc_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "tertile_loc_Medium", "tertile_loc_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_loc", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_loc",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "tertile_loc_Medium", "tertile_loc_High", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "tertile_loc_Medium", "tertile_loc_High"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "tertile_loc", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "tertile_loc",
#                         nlevels = 3))
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - tertile_diidensity
```{r 3 levels factor variable - tertile_diidensity d}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "tertile_diidensity_Medium", "tertile_diidensity_High", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "tertile_diidensity_Medium", "tertile_diidensity_High"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "tertile_diidensity", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "tertile_diidensity",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "tertile_diidensity_Medium", "tertile_diidensity_High", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "tertile_diidensity_Medium", "tertile_diidensity_High"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "tertile_diidensity", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "tertile_diidensity",
#                         nlevels = 3))
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - BMI_recent_grp
```{r 3 levels factor variable - BMI_recent_grp d}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_recent_grp",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "BMI_recent_grp_25_29", "BMI_recent_grp_sup_eq_30"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "BMI_recent_grp",
#                         nlevels = 3))
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

## 3 levels factor variable - BMI_YA_grp
```{r 3 levels factor variable - BMI_YA_grp d}
risk_ass <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25", ":"))
    risk <- eh_test_subtype(label = type,
                M = 2,
                factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25"),
                data = data)

    print(risk[["or_ci_p"]])

    print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_YA_grp",
                        nlevels = 3))
}
```

### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_stroma.i")
```
### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD3_CD8_stroma.i")
```
### CD11b_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_tumor.i")
```
### CD11b_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_total.i")
```
### CD11b_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_stroma.i")
```
### CD11b_CD15_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_tumor.i")
```
### CD11b_CD15_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD11b_CD15_total.i")
```
### CD11b_CD15_stroma.i
```{r}
risk_ass(data = ctrl_case_stroma, type = "CD11b_CD15_stroma.i")
```
### immunoscore_2018lancet_patients
```{r}
# risk_ass <- function(data, type){
# 
#     print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25", ":"))
#     risk <- eh_test_subtype(label = type,
#                 M = 3,
#                 factors = list("refage", "site", "fullpregnum", "ocdur", "tubelig", "famhist_br_ov", "prop_tumor", "BMI_YA_grp_20_24", "BMI_YA_grp_sup_eq_25"),
#                 data = data)
# 
#     print(risk[["or_ci_p"]])
# 
#     print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))
# 
#     print(posthoc_factor_test(fit = risk,
#                         factor = "BMI_YA_grp",
#                         nlevels = 3))
# }
# 
# risk_ass(data = ctrl_case_imm, type = "immunoscore_2018lancet_patients")
```
<br>
<br>

***

# VIb. Secondary analysis - Case only

```{r}
markers_wTMA_cases <- markers_wTMA %>%
  filter(casecon == "Case")
```

## 1.Distribution
Use plot from before unless we want an updated distribution with values of intratumoral + TMA combined
```{r}
```

## 2b.Logistic regression on category variables adjusted by age + site + fullpregnum + ocdur + tubelig + famhist_br_ov + prop_tumor
Results are exponentiated.

### 2 categories var
The regression on peripheral immune markers will not change when adding the TMA as we added TMA as intratumoral region.
```{r log reg function d}
loreg_table_int <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_remove(., "_")

    tbl1 <- glm(data[[paste0(type, ".i")]] ~ data[[i]] + refage + site + fullpregnum + ocdur + tubelig + famhist_br_ov + prop_tumor,
                data = data, family = "binomial") %>%
            tbl_regression(exponentiate = TRUE,
                           intercept = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Intratumoral"))
    print(tbl1)

  }
}
```

#### CD3_total

<div class = "row">
<div class = "col-md-6">
```{r log reg intrab, results = 'asis'}
loreg_table_int(data = markers_wTMA_cases, type = "CD3_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

#### CD3_CD8_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_wTMA_cases, type = "CD3_CD8_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

#### CD3_FoxP3_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_wTMA_cases, type = "CD3_FoxP3_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

#### CD11b_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_wTMA_cases, type = "CD11b_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

***

#### CD11b_CD15_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_wTMA_cases, type = "CD11b_CD15_total")
```
</div>

<div class = "col-md-6">
```{r}
```
</div>
</div>

<br>

***
***

<br>

### Immunoscore 3 cat 2018-lancet
TMA cannot be included in the immunoscore categories aka take previous values on ROI only.   
<br>

***
***

<br>
<br>

# 3b. Logistic regression on Continuous variables adjusted by age + site + fullpregnum + ocdur + tubelig + famhist_br_ov + prop_tumor
The regression on peripheral immune markers will not change when adding the TMA as we added TMA as intratumoral region.
```{r glm function d}
glm_table_int <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_replace(., "_", " ")

    tbl1 <- glm(data[[paste0(type, ".i")]] ~ data[[i]] + refage + site + fullpregnum + ocdur + tubelig + famhist_br_ov + prop_tumor,
                data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Intratumoral"))
    print(tbl1)

  }
}
```

## CD3_total

<div class = "row">
<div class = "col-md-6">
```{r glm intra d, results = 'asis'}
glm_table_int(data = markers_wTMA_cases, type = "percent_CD3_total")
```
</div>

<div class = "col-md-6">
```{r glm periph d, results = 'asis'}
```
</div>
</div>

***

## CD3_CD8_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_wTMA_cases, type = "percent_CD3_CD8_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
```
</div>
</div>

***

## CD3_FoxP3_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_wTMA_cases, type = "percent_CD3_FoxP3_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
```
</div>
</div>

***

## CD11b_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_wTMA_cases, type = "percent_CD11b_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
```
</div>
</div>

***

## CD11b_CD15_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_wTMA_cases, type = "percent_CD11b_CD15_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
```
</div>
</div>
<br>
<br>

***
***











