---
title: "Investigate data"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean #darkly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
h1.title {
  font-size: 25px;
}
.figure {
   margin-top: 25px;
   margin-bottom: 25;
}

table {
    margin-top: 25px;
    margin-bottom: 10px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Association between pre-diagnostic inflammatory-related exposures and immune cell abundance</span>

</div>
<br>

```{r library, include=FALSE}
library(tidyverse)
library(fastDummies)
library(data.table)
library(labelled)
library(nnet)
library(gtsummary)
library(ggplot2)
library(survival)
library(survminer)
library(mclust)
library(gplots)
library(riskclustr)
```

```{r load}
markers_ROI <- readRDS(paste0(here::here(), "/markers_ROI_category.rds"))
```

```{r}
var_label(markers_ROI) <- list(refage ~ "Age at diagnosis", refage_cat ~ "Age at diagnosis category",
                           smokcurrent ~ "Smoking status"
) 
```


# I. Data exploration
## Compare patient characteristics for patients with vs. without immune data
```{r Compare patient}
no_immune_data <- markers_ROI %>% filter(is.na(percent_CD3_total.i) & is.na(percent_CD3_total.p))
have_immune_data <- markers_ROI %>% filter(!is.na(percent_CD3_total.i) | !is.na(percent_CD3_total.p))

markers_ROI %>% 
  mutate(have_immune_data = case_when(
    !is.na(percent_CD3_total.i) | 
      !is.na(percent_CD3_total.p)        ~ "Have immune data",
    TRUE                                 ~ "No immune data"
  )) %>% 
  filter(casecon == "Case") %>% 
  select(diagyear, refage, refage_cat, 
         histotype, histotype1, histotype2,
         smokever, smokcurrent,
         packyrs, packyrs_cat, 
         BMI_recent_grp, BMI_YA_grp, 
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta, 
         inactive, paga, loc,
         education,diidensity, diidenswithsupp,
         perceived_discrim, phys_trust,
         have_immune_data) %>% 
  tbl_summary(by = have_immune_data,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels() %>% 
  add_overall() %>% add_p() %>% bold_p(t= .05)

no_immune_data <- no_immune_data %>% 
  select(diagyear, refage, refage_cat, 
         histotype, histotype1, histotype2,
         smokever, smokcurrent,
         packyrs, packyrs_cat, 
         BMI_recent_grp, BMI_YA_grp, 
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta, 
         inactive, paga, loc,
         education,diidensity, diidenswithsupp,
         perceived_discrim, phys_trust,
         casecon) %>% 
  tbl_summary(by = casecon,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels()

have_immune_data <- have_immune_data %>% 
  select(diagyear, refage, refage_cat, 
         histotype, histotype1, histotype2,
         smokever, smokcurrent,
         packyrs, packyrs_cat, 
         BMI_recent_grp, BMI_YA_grp, 
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta, 
         inactive, paga, loc,
         education,diidensity, diidenswithsupp,
         perceived_discrim, phys_trust,
         casecon) %>% 
  tbl_summary(by = casecon,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)) %>%
  bold_labels()

tbl_merge(list(no_immune_data, have_immune_data), tab_spanner = c("no_immune_data", "have_immune_data"))
```

```{r Clean pop}
markers_ROI <- markers_ROI %>% filter(casecon == "Control" |
                                        !is.na(percent_CD3_total.i) | 
                                        !is.na(percent_CD3_total.p))
```

### From here, the analysis include only control patients and cases with immune data patients.

## 1. Patient characteristics
```{r patient table}
markers_ROI %>% 
  select(diagyear, refage, refage_cat, 
         histotype, histotype1, histotype2,
        casecon) %>% 
  tbl_summary(by = casecon,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)) %>%
      # modify_header(list(label ~ "**Patient characteristics**", all_stat_cols() ~ "**{level}**, N = {n}")) %>% 
  bold_labels()
```

## 1. Patient characteristics
```{r patient table}
markers_ROI %>% 
  select(starts_with("CD"), immunoscore_2018lancet_patients) %>% 
  tbl_summary(
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              digits = list(all_continuous() ~ 1)) %>%
      # modify_header(list(label ~ "**Patient characteristics**", all_stat_cols() ~ "**{level}**, N = {n}")) %>% 
  bold_labels()
```

# 3. Distribution of the potential inflammatory-related pre-diagnostic exposures in the overall study population and by immune abundance (only use overall intratumoral and overall peritumoral), immune signatures, and immunoscore

## Summary table
```{r exposures table}
markers_ROI %>% 
  select(smokever, smokcurrent,
         packyrs, packyrs_cat, 
         BMI_recent_grp, BMI_YA_grp, 
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta, 
         inactive, paga, loc,
         education,diidensity, diidenswithsupp,
         perceived_discrim, phys_trust,
         casecon) %>% 
  tbl_summary(by = casecon,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              # label = list(refage ~ "Age at diagnosis", refage_cat ~ "Age at diagnosis category",
              #              dblkstat_CA125 ~ "Debulking Status", adj ~ "Adjuvant chemotherapy",
              #              smokcurrent ~ "Smoking status"),
              # type = list(c(diab,
              #   talcever, talcgen, talcnongen,
              #               aspirin, NSAID,aceta, 
              #               hyster, hyster1yr,
              #               hyster2yr, hystertype,
              #               tubelig, endomet, fibroids,
              #               pid, education) ~ "categorical"),
              digits = list(all_continuous() ~ 1)
  ) %>%
  # modify_header(list(label ~ "**Patient Exposure characteristics**", all_stat_cols() ~ "**{level}**, N = {n}")) %>% 
  bold_labels()
```

## Intratumoral CD3 total - Overall pop
```{r}
markers_ROI %>% 
  distinct(suid, .keep_all = TRUE) %>% 
  select(smokever, smokcurrent,
         packyrs, packyrs_cat, 
         BMI_recent_grp, BMI_YA_grp, 
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta, 
         inactive, paga, loc,
         education,diidensity, diidenswithsupp,
         perceived_discrim, phys_trust,
         CD3_total.i) %>% 
  tbl_summary(by = CD3_total.i,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              # type = list(c(diab,
              #   talcever, talcgen, talcnongen,
              #               aspirin, NSAID,aceta,
              #               hyster, hyster1yr,
              #               hyster2yr, hystertype,
              #               tubelig, endomet, fibroids,
              #               pid, education) ~ "categorical"),
              digits = list(all_continuous() ~ 1)
  ) %>%
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
```

## Intratumoral CD3CD8 total - Overall pop
```{r}
markers_ROI %>% 
  distinct(suid, .keep_all = TRUE) %>% 
  select(smokever, smokcurrent,
         packyrs, packyrs_cat, 
         BMI_recent_grp, BMI_YA_grp, 
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta, 
         inactive, paga, loc,
         education,diidensity, diidenswithsupp,
         perceived_discrim, phys_trust,
         CD3_CD8_total.i) %>% 
  tbl_summary(by = CD3_CD8_total.i,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              # type = list(c(diab,
              #   talcever, talcgen, talcnongen,
              #               aspirin, NSAID,aceta,
              #               hyster, hyster1yr,
              #               hyster2yr, hystertype,
              #               tubelig, endomet, fibroids,
              #               pid, education) ~ "categorical"),
              digits = list(all_continuous() ~ 1)
  ) %>%
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
```

## Intratumoral Immunoscore - Overall pop
```{r}
markers_ROI %>% 
  distinct(suid, .keep_all = TRUE) %>% 
  select(smokever, smokcurrent,
         packyrs, packyrs_cat, 
         BMI_recent_grp, BMI_YA_grp, 
         endomet, pid, fibroids,
         talcever, talcgen, talcnongen,
         diab, hrtdis, hbp, hchol,
         aspirin, NSAID, aceta, 
         inactive, paga, loc,
         education,diidensity, diidenswithsupp,
         perceived_discrim, phys_trust,
         immunoscore_2018lancet_patients) %>% 
  tbl_summary(by = immunoscore_2018lancet_patients,
              statistic = list(all_continuous() ~ "{mean} ({sd})"),
              # type = list(c(diab,
              #   talcever, talcgen, talcnongen,
              #               aspirin, NSAID,aceta,
              #               hyster, hyster1yr,
              #               hyster2yr, hystertype,
              #               tubelig, endomet, fibroids,
              #               pid, education) ~ "categorical"),
              digits = list(all_continuous() ~ 1)
  ) %>%
  add_overall() %>% bold_labels() %>% add_p() %>% bold_p(t = .05) %>% as_gt()
```

```{r}
exposure_var <- c("smokever", "smokcurrent",
                  "packyrs", "packyrs_cat", 
                  "BMI_recent_grp", "BMI_YA_grp", 
                  "endomet", "pid", "fibroids",
                  "talcever", "talcgen", "talcnongen",
                  "diab", "hrtdis", "hbp", "hchol",
                  "aspirin", "NSAID", "aceta", 
                  "inactive", "paga", "loc",
                  "education","diidensity", "diidenswithsupp",
                  "perceived_discrim", "phys_trust"
                  ) 
```

## Violin plots
```{r violin}
violin_plot <- function(data, type){

  for (i in exposure_var){

    if(class(markers_ROI[[i]]) == "factor" | class(markers_ROI[[i]]) == "character") {

      p1 <- markers_ROI %>%
        filter(!is.na(.data[[i]])) %>% 
        ggplot()+
        geom_violin(aes(x=.data[[i]], y= .data[[paste0(type, ".i")]]), scale = "count")+
        geom_boxplot(aes(x=.data[[i]], y= .data[[paste0(type, ".i")]]), width=.1) +
        theme_classic()+
        labs(y=NULL, title="Intratumoral \nROIs")
      p2 <- markers_ROI %>%
        filter(!is.na(.data[[i]])) %>% 
        ggplot()+
        geom_violin(aes(x=.data[[i]], y= .data[[paste0(type, ".p")]]), scale = "count")+
        geom_boxplot(aes(x=.data[[i]], y= .data[[paste0(type, ".p")]]), width=.1) +
        theme_classic()+
        labs(y=NULL, title="Peripheral \nROIs")

      main <- str_match(type, "percent_(.*)_total")[,2]
      gridExtra::grid.arrange(p1, p2, ncol = 2,
                              top = "% of Cells Present in",
                              left =  paste("Overall", main, "immune cells (%) per patients"),
                              bottom = "Data on Race-Matched Patients")
    }
  }
}
```

### CD3
```{r}
violin_plot(data = markers_ROI, type = "percent_CD3_total")
```

### CD3 CD8
```{r}
violin_plot(data = markers_ROI, type = "percent_CD3_CD8_total")
```

### CD3 FoxP3
```{r}
violin_plot(data = markers_ROI, type = "percent_CD3_FoxP3_total")
```

### C11b
```{r}
violin_plot(data = markers_ROI, type = "percent_CD11b_total")
```

### CD11b CD15
```{r}
violin_plot(data = markers_ROI, type = "percent_CD11b_CD15_total")
```

## Scatter plots
```{r point}
point_plot <- function(data, type){

  for (i in exposure_var){

    if(class(markers_ROI[[i]]) == "numeric" | class(markers_ROI[[i]]) == "integer") {

      p1 <- markers_ROI %>%
        ggplot(aes(x=.data[[i]], y= .data[[paste0(type, ".i")]]))+
        geom_point()+
        geom_smooth(method = "lm", se = FALSE)+
        stat_regline_equation(label.y.npc = 1)+
        theme_classic()+
        labs(y=NULL, title="Intratumoral \nROIs")
      p2 <- markers_ROI %>%
        ggplot(aes(x=.data[[i]], y= .data[[paste0(type, ".p")]]))+
        geom_point()+
        geom_smooth(method = "lm", se = FALSE)+
        stat_regline_equation(label.y.npc = 1)+
        theme_classic()+
        labs(y=NULL, title="Peripheral \nROIs")

      main <- str_match(type, "percent_(.*)_total")[,2] %>%
        str_remove(., "_")
      gridExtra::grid.arrange(p1, p2, ncol = 2,
                              top = "% of Cells Present in",
                              left =  paste("Overall", main, "immune cells (%) per patients"),
                              bottom = "Data on Race-Matched Patients")
    }
  }
}
```

### CD3
```{r}
point_plot(data = markers_ROI, type = "percent_CD3_total")
```

### CD3 CD8
```{r}
point_plot(data = markers_ROI, type = "percent_CD3_CD8_total")
```

### CD3 FoxP3
```{r}
point_plot(data = markers_ROI, type = "percent_CD3_FoxP3_total")
```

### CD11b
```{r}
point_plot(data = markers_ROI, type = "percent_CD11b_total")
```

### CD11b CD15
```{r}
point_plot(data = markers_ROI, type = "percent_CD11b_CD15_total")
```
<br>
<br>

***
***

<br>

# II. Logistic regression adjusted by age + site

```{r log reg function}
loreg_table_int <- function(data, type){
  
  for (i in exposure_var){
    
    main <- str_match(type, "(.*)_total")[,2] %>% 
      str_remove(., "_")
    
    tbl1 <- glm(data[[paste0(type, ".i")]] ~ data[[i]] + refage + site, 
                data = data, family = "binomial") %>%
            tbl_regression(exponentiate = TRUE, 
                           label = list(`data[[i]]` ~ i)) %>% 
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Intratumoral"))
    print(tbl1)
    
  }
}

loreg_table_per <- function(data, type){

  for (i in exposure_var){

    main <- str_match(type, "(.*)_total")[,2] %>%
      str_remove(., "_")

    tbl2 <- glm(data[[paste0(type, ".p")]] ~ data[[i]] + refage + site, 
                data = data, family = "binomial") %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Peripheral"))
    print(tbl2)

  }
}
```

## Overall

### CD3_total

<div class = "row">
<div class = "col-md-6">
```{r log reg intra, results = 'asis'}
loreg_table_int(data = markers_ROI, type = "CD3_total")
```
</div>

<div class = "col-md-6">
```{r log reg periph, results = 'asis'}
# loreg_table_per(data = markers_ROI, type = "CD3_total")
```
</div>
</div>

***

### CD3_CD8_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_ROI, type = "CD3_CD8_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_ROI, type = "CD3_CD8_total")
```
</div>
</div>

***

### CD3_FoxP3_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_ROI, type = "CD3_FoxP3_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_ROI, type = "CD3_FoxP3_total")
```
</div>
</div>

***

### CD11b_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_ROI, type = "CD11b_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_ROI, type = "CD11b_total")
```
</div>
</div>

***

### CD11b_CD15_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
loreg_table_int(data = markers_ROI, type = "CD11b_CD15_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_per(data = markers_ROI, type = "CD11b_CD15_total")
```
</div>
</div>

<br>

***
***

<br>

<!-- ## Immunoscore -->

```{r multi reg function}
multinom_pivot_wider <- function(x) {
  # check inputs match expectatations
  if (!inherits(x, "tbl_regression") || !inherits(x$model_obj, "multinom")) {
    stop("`x=` must be class 'tbl_regression' summary of a `nnet::multinom()` model.")
  }

  # create tibble of results
  df <- tibble::tibble(outcome_level = unique(x$table_body$groupname_col))
  df$tbl <-
    purrr::map(
      df$outcome_level,
      function(lvl) {
        gtsummary::modify_table_body(
          x,
          ~dplyr::filter(.x, .data$groupname_col %in% lvl) %>%
            dplyr::ungroup() %>%
            dplyr::select(-.data$groupname_col)
        )
      }
    )

  tbl_merge(df$tbl, tab_spanner = paste0("**", df$outcome_level, "**"))
}

multireg_table_int <- function(data){

  for (i in exposure_var){

    tbl1 <- multinom(immunoscore_2018lancet_patients ~ data[[i]] + refage + site,
                     data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
  multinom_pivot_wider() #%>%
            # modify_spanning_header(everything() ~ paste("Association with Overall", "immunoscore_patients", "Intratumoral"))
    print(tbl1)

  }
}

multireg_table_per <- function(data, type){

  for (i in exposure_var){

    tbl2 <- multinom(immunoscore_2018lancet_patients ~ data[[i]] + refage + site,
                     data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
  multinom_pivot_wider()# %>%
            # modify_spanning_header(everything() ~ paste("Association with Overall", "immunoscore_patients", "Peripheral"))
    print(tbl2)

  }
}
```
<!-- Intratumoral -->

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}

# model <- multinom(immunoscore_patients ~ BMI_recent_grp, data = markers_ROI)
# broom::tidy(model)
# exp(coef(model))
# multinom(immunoscore_patients ~ BMI_recent_grp, data = markers_ROI) %>%
#   tbl_regression(exponentiate = TRUE) %>%
#   multinom_pivot_wider()

# multireg_table_int(data = markers_ROI)
```
</div>

<!-- Peripheral  -->

<div class = "col-md-6">
```{r, results = 'asis'}
# multireg_table_per(data = markers_ROI)
```
</div>
</div>

# Immunoscore 3 cat 2018lancet

What are the weight?
```{r}
multinom(immunoscore_2018lancet_patients ~ immunoscore_2018lancet_patients + refage + site,
                     data = markers_ROI)
```

```{r multi reg}
multireg_table_int <- function(data){

  for (i in exposure_var){

    tbl1 <- multinom(immunoscore_2018lancet_patients ~ data[[i]] + refage + site,
                     data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
  multinom_pivot_wider()# %>%
            # modify_spanning_header(everything() ~ paste("Association with Overall", "immunoscore_patients", "Intratumoral"))
    print(tbl1)

  }
}

multireg_table_per <- function(data){

  for (i in exposure_var){

    tbl2 <- multinom(immunoscore_2018lancet_patients ~ data[[i]] + refage + site,
                     data = data) %>%
            tbl_regression(exponentiate = TRUE,
                           label = list(`data[[i]]` ~ i)) %>%
  multinom_pivot_wider()# %>%
            # modify_spanning_header(everything() ~ paste("Association with Overall", "immunoscore_patients", "Peripheral"))
    print(tbl2)

  }
}
```

## Overall

### Intratumoral

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
multireg_table_int(data = markers_ROI)
```
</div>

### Peripheral

<div class = "col-md-6">
```{r, results = 'asis'}
multireg_table_per(data = markers_ROI)
```
</div>
</div>

<br>

***
***

<br>
<br>

# III. Risk assessement
## Overall population
```{r dummy}
markers_ROI <- markers_ROI %>% 
  mutate_at(c("CD3_tumor.i", "CD3_total.i", "CD3_stroma.i", 
              "CD3_CD8_tumor.i", "CD3_CD8_total.i", "CD3_CD8_stroma.i"), 
            ~ case_when(
              is.na(.)                                               ~ 0,
              . == "low"                                             ~ 1,
              . == "high"                                            ~ 2,
            ))

ctrl_case <- dummy_cols(markers_ROI, 
                        select_columns = 
                          c(#"smokever", 
                            "smokcurrent",
                            "packyrs_cat"#,
                            # "BMI_YA_2grp",
                            # "endomet", "pid", "fibroids",
                            # "talcever", "talcgen", "talcnongen",
                            # "diab", "hrtdis", "hbp", "hchol",
                            # "aspirin", "NSAID", "aceta",
                            # "inactive", "paga",
                            # "education"
                            ))

colnames(ctrl_case)
```

### 2 levels factor variable
```{r 2 levels factor variable}
factor_name <- c("smokever", 
                 "endomet", "pid", "fibroids",
                 "talcever", "talcgen", "talcnongen",
                 "diab", "hrtdis", "hbp", "hchol",
                 "aspirin", "NSAID", "aceta",
                 "inactive", "paga",
                 "education",
                 "diidensity", "diidenswithsupp",
                 "perceived_discrim", "phys_trust",
                 "BMI_YA_2grp")

risk_ass <- function(data, type){

  for (i in factor_name){

    print(paste("RISK ASSESSMENT FOR ->", i, ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "site", i), 
                data = data)

    print(risk[["or_ci_p"]])

  }
}
```

#### CD3_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor.i")
```
#### CD3_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_total.i")
```
#### CD3_stroma.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_stroma.i")
```
#### CD3_CD8_tumor.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
#### CD3_CD8_total.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_total.i")
```
#### CD3_CD8_stroma.i
```{r}
risk_ass(data = ctrl_case, type = "CD3_CD8_stroma.i")
```

### 3 levels factor variable - smokcurrent
```{r 3 levels factor variable - smokcurrent}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "site", "smokcurrent_current", "smokcurrent_former"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "smokcurrent",
                        nlevels = 3))
}
```

#### CD3_tumor.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_tumor.i")
```
#### CD3_total.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_total.i")
```
#### CD3_stroma.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_stroma.i")
```
#### CD3_CD8_tumor.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
#### CD3_CD8_total.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_CD8_total.i")
```
#### CD3_CD8_stroma.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_CD8_stroma.i")
```

### 3 levels factor variable - packyrs_cat
```{r 3 levels factor variable - packyrs_cat}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "site", "packyrs_cat_inf_eq_15", "packyrs_cat_sup_15"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "packyrs_cat", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "packyrs_cat",
                        nlevels = 3))
}
```

#### CD3_tumor.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_tumor.i")
```
#### CD3_total.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_total.i")
```
#### CD3_stroma.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_stroma.i")
```
#### CD3_CD8_tumor.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_CD8_tumor.i")
```
#### CD3_CD8_total.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_CD8_total.i")
```
#### CD3_CD8_stroma.i
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_CD8_stroma.i")
```
<br>
<br>

***

# Secondary analysis
## Distribution
```{r distribution, fig.height=12, fig.width=12}
markers_ROI %>% 
  select(starts_with("percent_CD3"), starts_with("percent_CD11b")) %>% 
  pivot_longer(cols = everything()) %>% 
  mutate(region = case_when(
    str_detect(name, ".i")           ~ "intratumoral",
    str_detect(name, ".p")           ~ "peripheral"
  )) %>% 
  mutate(compartment = case_when(
    str_detect(name, "tumor")           ~ "tumor",
    str_detect(name, "stroma")           ~ "stroma",
    str_detect(name, "total")           ~ "total"
  )) %>% 
  mutate(marker = str_match(name, "percent_(.*)(_total|_tumor|_stroma)")[,2]) %>% 
  ggplot(aes(value, color= compartment, fill= compartment))+
  geom_density(alpha=.5)+
  theme_classic()+
  facet_wrap(region ~ marker, scales = "free", nrow = 2) +
  theme(legend.position="bottom")
```

## Glm
```{r glm function}
glm_table_int <- function(data, type){
  
  for (i in exposure_var){
    
    main <- str_match(type, "(.*)_total")[,2] %>% 
      str_replace(., "_", " ")
    
    tbl1 <- glm(data[[paste0(type, ".i")]] ~ data[[i]] + refage + site, 
                data = data) %>%
            tbl_regression(exponentiate = TRUE, 
                           label = list(`data[[i]]` ~ i)) %>% 
            modify_spanning_header(everything() ~ paste("Association with Overall", main, "Intratumoral"))
    print(tbl1)
    
  }
}
```
## Overall

### CD3_total

<div class = "row">
<div class = "col-md-6">
```{r glm intra, results = 'asis'}
glm_table_int(data = markers_ROI, type = "percent_CD3_total")
```
</div>

<div class = "col-md-6">
```{r glm periph, results = 'asis'}
# glm_table_(data = markers_ROI, type = "CD3_total")
```
</div>
</div>

***

### CD3_CD8_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_ROI, type = "CD3_CD8_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# glm_table_(data = markers_ROI, type = "CD3_CD8_total")
```
</div>
</div>

***

### CD3_FoxP3_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_ROI, type = "CD3_FoxP3_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# glm_table_(data = markers_ROI, type = "CD3_FoxP3_total")
```
</div>
</div>

***

### CD11b_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_ROI, type = "CD11b_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# glm_table_(data = markers_ROI, type = "CD11b_total")
```
</div>
</div>

***

### CD11b_CD15_total

<div class = "row">
<div class = "col-md-6">
```{r, results = 'asis'}
glm_table_int(data = markers_ROI, type = "CD11b_CD15_total")
```
</div>

<div class = "col-md-6">
```{r, results = 'asis'}
# loreg_table_(data = markers_ROI, type = "CD11b_CD15_total")
```
</div>
</div>

<br>

***
***


***



