---
title: "Risk assessment"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: cerulean #darkly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

<style type="text/css">
h1.title {
  font-size: 25px;
}
.figure {
   margin-top: 25px;
   margin-bottom: 25;
}

table {
    margin-top: 25px;
    margin-bottom: 10px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      # fig.width = 7, fig.height = 5, 
                      fig.align='center'#, fig.show='hold'
                      )
options(gtsummary.print_engine = "gt")
options(gtsummary.as_gt.addl_cmds = "gt::tab_options(table.font.size = 14, data_row.padding = gt::px(1))")
```

<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">Risk assessment inflammatory-related exposures and immune cell abundance</span>

</div>
<br>

```{r library, include=FALSE}
# library(drake)
library(tidyverse)
library(data.table)
library(nnet)
library(gtsummary)
library(survival)
library(survminer)
library(mclust)
library(gplots)
```

# Risk assessement
## Overall population
```{r}
library(riskclustr)

ctrl_case <- read_csv(paste0(here::here(), "/DataforChristelle.csv")) %>% 
  `colnames<-`(str_remove_all(colnames(.), " kg/m2|-") %>% 
                 str_replace_all(., ">", "sup")) %>% 
  mutate(BMI_YA_2grp = case_when(
    BMI_YA_grp == "<25 kg/m2"           ~ "<25 kg/m2",
    BMI_YA_grp == "25-30 kg/m2" |
      BMI_YA_grp == ">30 kg/m2"         ~ "≥25 kg/m2"
  ))

# ctrl_case <- ctrl_case %>% 
#   mutate(smokcurrent = case_when(
#     smokcurrent == "never"      ~ 1,
#     smokcurrent == "former"      ~ 2,
#     smokcurrent == "current"      ~ 3
#   ),
#   smokcurrent = factor(smokcurrent))

colnames(ctrl_case)
```

### 2 levels factor variable
```{r}
factor_name <- c("BMI_YA_2grp", "talcever", "endomet", "fibroids", "pid",
                 "smokever", "aspirin")

risk_ass <- function(data, type){

  for (i in factor_name){

    print(paste("RISK ASSESSMENT FOR ->", i, ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "race", i), 
                data = data)

    print(risk[["or_ci_p"]])

  }
}
```

#### CD3_tumor_cat
```{r}
risk_ass(data = ctrl_case, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass(data = ctrl_case, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass(data = ctrl_case, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass(data = ctrl_case, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass(data = ctrl_case, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass(data = ctrl_case, type = "CD3CD8_stroma_cat")
```

### 3 levels factor variable - BMI recent
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_2530", "BMI_recent_grp_sup30", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "race", "BMI_recent_grp_2530", "BMI_recent_grp_sup30"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_recent_grp",
                        nlevels = 3))
}
```

#### CD3_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3CD8_stroma_cat")
```

### 3 levels factor variable - BMI YA
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_2530", "BMI_YA_grp_sup30", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "race", "BMI_YA_grp_2530", "BMI_YA_grp_sup30"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_YA_grp",
                        nlevels = 3))
}
```

#### CD3_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3CD8_stroma_cat")
```

### 3 levels factor variable - smokcurrent
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "race", "smokcurrent_current", "smokcurrent_former"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "smokcurrent",
                        nlevels = 3))
}
```

#### CD3_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case, type = "CD3CD8_stroma_cat")
```

```{r}
# risk <- eh_test_subtype(label = "CD3_tumor_cat", 
#                 M = 2, 
#                 factors = list("refage", "race", 
#                                "smokcurrent_current", 
#                                "smokcurrent_former"), 
#                 data = ctrl_case)
# risk
# 
# posthoc_factor_test(fit = risk,
#                     factor = "smokcurrent_current",
#                     nlevels = 2)
# 
# 
# risk <- eh_test_subtype(label = "CD3_tumor_cat",
#                 M = 2,
#                 factors = list("refage", "race",
#                                "smokcurrent_former",
#                                "smokcurrent_current"),
#                 data = ctrl_case)
# risk
# 
# posthoc_factor_test(fit = risk,
#                     factor = "smokcurrent",
#                     nlevels = 3)
```
<br>
<br>

***

## White
```{r}
ctrl_case_white <- ctrl_case %>% 
  filter(race == "White")
```

### 2 levels factor variable
```{r}
risk_ass <- function(data, type){

  for (i in factor_name){

    print(paste("RISK ASSESSMENT FOR ->", i, ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", i), 
                data = data)

    print(risk[["or_ci_p"]])

  }
}
```

#### CD3_tumor_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3CD8_stroma_cat")
```

### 3 levels factor variable - BMI recent
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_2530", "BMI_recent_grp_sup30", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "BMI_recent_grp_2530", "BMI_recent_grp_sup30"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_recent_grp",
                        nlevels = 3))
}
```

#### CD3_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_stroma_cat")
```

### 3 levels factor variable - BMI YA
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_2530", "BMI_YA_grp_sup30", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "BMI_YA_grp_2530", "BMI_YA_grp_sup30"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_YA_grp",
                        nlevels = 3))
}
```

#### CD3_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_stroma_cat")
```

### 3 levels factor variable - smokcurrent
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "smokcurrent_current", "smokcurrent_former"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "smokcurrent",
                        nlevels = 3))
}
```

#### CD3_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_stroma_cat")
```
<br>
<br>

***

## Black
```{r}
ctrl_case_white <- ctrl_case %>% 
  filter(race == "Black")
```

### 2 levels factor variable
```{r}
risk_ass <- function(data, type){

  for (i in factor_name){

    print(paste("RISK ASSESSMENT FOR ->", i, ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", i), 
                data = data)

    print(risk[["or_ci_p"]])

  }
}
```

#### CD3_tumor_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass(data = ctrl_case_white, type = "CD3CD8_stroma_cat")
```

### 3 levels factor variable - BMI recent
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_recent_grp_2530", "BMI_recent_grp_sup30", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "BMI_recent_grp_2530", "BMI_recent_grp_sup30"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "BMI_recent_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_recent_grp",
                        nlevels = 3))
}
```

#### CD3_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_stroma_cat")
```

### 3 levels factor variable - BMI YA
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "BMI_YA_grp_2530", "BMI_YA_grp_sup30", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "BMI_YA_grp_2530", "BMI_YA_grp_sup30"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "BMI_YA_grp", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "BMI_YA_grp",
                        nlevels = 3))
}
```

#### CD3_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_stroma_cat")
```

### 3 levels factor variable - smokcurrent
```{r}
risk_ass_bmi <- function(data, type){

    print(paste("RISK ASSESSMENT FOR ->", "smokcurrent_current", "smokcurrent_former", ":"))
    risk <- eh_test_subtype(label = type, 
                M = 2, 
                factors = list("refage", "smokcurrent_current", "smokcurrent_former"), 
                data = data)

    print(risk[["or_ci_p"]])
    
    print(paste("OVERALL PVAL FOR ->", "smokcurrent", ":"))

    print(posthoc_factor_test(fit = risk,
                        factor = "smokcurrent",
                        nlevels = 3))
}
```

#### CD3_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_tumor_cat")
```
#### CD3_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_total_cat")
```
#### CD3_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3_stroma_cat")
```
#### CD3CD8_tumor_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_tumor_cat")
```
#### CD3CD8_total_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_total_cat")
```
#### CD3CD8_stroma_cat
```{r}
risk_ass_bmi(data = ctrl_case_white, type = "CD3CD8_stroma_cat")
```
<br>
<br>

***


